---
title: "Tennis matches prediction"
author: "Minh Trung (James) Vo"
date: "2024-11-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(dplyr, 
               data.table, 
               LaplacesDemon, 
               readr, 
               Hmisc, 
               corrplot, 
               lattice, 
               patchwork, 
               ggplot2, 
               tidyverse, 
               tidymodels, 
               cluster, 
               factoextra, 
               purrr, 
               reshape2, 
               datetime, 
               dplyr, 
               plyr, 
               ggpubr)

```


# DATA SET UP, MODEL FUNCTIONS


```{r}
### Read the data and extract necessary variables
tennis <- read.csv("~/UoA/Project A/tennis_1968_2019.csv")


tennis <- tennis %>% 
  select(c(
    "tourney_date",
    "tourney_name",
    "surface",
    "draw_size",
    "tourney_level",
    "match_num",
    "winner_id",
    "loser_id",
    "best_of",
    "winner_rank",
    "winner_rank_points",
    "loser_rank",
    "loser_rank_points")) |>
  mutate_at(
    c("tourney_name", "surface","best_of"),
    as.factor) |>
  mutate_at(c("winner_id", "loser_id"), as.integer) |>
  mutate(tourney_date = ymd(tourney_date))



### re-order by date

attach(tennis)

tennis <- tennis[order(tourney_date),]

detach(tennis)

tennis <- tennis %>%
  filter (winner_id != 199999 & loser_id != 199999)



### Adding match ID for easier merging and cleaning
tennis <- tibble::rowid_to_column(tennis, "match_id")


### Splitting data to surface type for later use in Surface Elo

tennis_carpet <- tennis %>%
  filter (surface == "Carpet")


tennis_clay <- tennis %>%
  filter (surface == "Clay")


tennis_grass <- tennis %>%
  filter (surface == "Grass")


tennis_hard <- tennis %>%
  filter (surface == "Hard")

```



## ORIGINAL ELO FUNCTION
```{r}
## ORIGINAL ELO FUNCTION


### update elo after match
update_elo_ratings <- function(rating_a, rating_b, score_a, k = 31) {
  expected_score_a <- calculate_expected_score(rating_a, rating_b)
  new_rating_a <- rating_a + k * (score_a - expected_score_a)
  new_rating_b <- rating_b + k * ((1 - score_a) - (1 - expected_score_a))
  
  return(c(new_rating_a, new_rating_b))
}


### expected outcome
calculate_expected_score <- function(rating_a, rating_b) {
  return (1 / (1 + 10^((rating_b - rating_a) / 400)))
}


run_elo <- function (input_data, k = 31) {
  
  ## SET UP THE ELO TABLE
  player_elo_table <- NULL

  player_elo_table$player_id <- unique(c(input_data$winner_id, input_data$loser_id))

  player_elo_table <- as.data.frame(player_elo_table)

  player_elo_table$player_elo <- rep(1500)

  ## SET UP THE MATCH TABLE
  input_data$winner_pre_elo <- NA
  input_data$loser_pre_elo <- NA
  input_data$winner_post_elo <- NA
  input_data$loser_post_elo <- NA
  
  
  ## RUN THE ELO SEQ
  for (i in 1:nrow(input_data)) {
    # set the winner and loser of the match
    winner <- input_data$winner_id[i]
    loser <- input_data$loser_id[i]
    
    # call out player current elo
    input_data$winner_pre_elo[i] <-
      player_elo_table$player_elo[player_elo_table$player_id == winner]
    
    input_data$loser_pre_elo[i] <- 
      player_elo_table$player_elo[player_elo_table$player_id == loser]
    
    # calculate new rating and update player rating after the match
    new_ratings <- update_elo_ratings(input_data$winner_pre_elo[i],
                                      input_data$loser_pre_elo[i], 1, k)
    
    input_data$winner_post_elo[i] <- new_ratings[1]
    input_data$loser_post_elo[i] <- new_ratings[2]
  
    player_elo_table$player_elo[player_elo_table$player_id == winner] <-
      new_ratings[1]
    
    player_elo_table$player_elo[player_elo_table$player_id == loser] <-
      new_ratings[2]
    
    player_elo_table$player_matches[player_elo_table$player_id == winner] <- 
      winner_match +1
    
    player_elo_table$player_matches[player_elo_table$player_id == loser] <- 
      loser_match +1
  
  }
  return (list(input_data, player_elo_table))
}
```



## FTE ELO function
```{r} 

## FTE ELO function

update_elo_ratings_FTE <- function(rating_a, rating_b, score_a, k_a, k_b) { # FTE Elo use a dynamic k for each player
  expected_score_a <- calculate_expected_score(rating_a, rating_b)
  new_rating_a <- rating_a + k_a * (score_a - expected_score_a)
  new_rating_b <- rating_b + k_b * ((1 - score_a) - (1 - expected_score_a))
  
  return(c(new_rating_a, new_rating_b))
}

calculate_expected_score <- function(rating_a, rating_b) {
  return (1 / (1 + 10^((rating_b - rating_a) / 400)))
}


run_elo_FTE <- function (input_data, delta = 100, nu = 5, sigma = 0.1) {
  
  ## SET UP THE ELO TABLE
  player_elo_table <- NULL

  player_elo_table$player_id <- unique(c(input_data$winner_id, input_data$loser_id))

  player_elo_table <- as.data.frame(player_elo_table)

  player_elo_table$player_elo <- rep(1500)

  player_elo_table$player_matches <- rep(0)
  
  ## SET UP THE MATCH TABLE
  input_data$winner_pre_elo <- NA
  input_data$loser_pre_elo <- NA
  input_data$winner_post_elo <- NA
  input_data$loser_post_elo <- NA
  
  
  
  ## RUN THE ELO SEQ
  for (i in 1:nrow(input_data)) {
    winner <- input_data$winner_id[i]
    loser <- input_data$loser_id[i]
    
    # search for player and set their current elo and number of matches
    input_data$winner_pre_elo[i] <-
      player_elo_table$player_elo[player_elo_table$player_id == winner]
    
    input_data$loser_pre_elo[i] <- 
      player_elo_table$player_elo[player_elo_table$player_id == loser]
    
    
    winner_matches <- player_elo_table$player_matches[player_elo_table$player_id == winner]
    
    loser_matches <- player_elo_table$player_matches[player_elo_table$player_id == loser]
    
    # calculate k using the number of matches
    
    k_winner = delta / (winner_matches + nu)^sigma
    
    k_loser = delta / (loser_matches + nu)^sigma
    
    
    # calculate the rating after the match
    new_ratings <- update_elo_ratings_FTE(input_data$winner_pre_elo[i],
                                          input_data$loser_pre_elo[i], 
                                          1, 
                                          k_winner, 
                                          k_loser)
    
    # update the player elo after the match, and the number of match played
    input_data$winner_post_elo[i] <- new_ratings[1]
    input_data$loser_post_elo[i] <- new_ratings[2]
  
    player_elo_table$player_elo[player_elo_table$player_id == winner] <-
      new_ratings[1]
    
    player_elo_table$player_elo[player_elo_table$player_id == loser] <-
      new_ratings[2]
    
    player_elo_table$player_matches[player_elo_table$player_id == winner] <- 
      winner_matches +1
    
    player_elo_table$player_matches[player_elo_table$player_id == loser] <- 
      loser_matches +1
  
  }
  return (list(input_data, player_elo_table))
}


```


## SET UP THE BETTING DATA
```{r}
#### SET UP THE BETTING DATA. Most of the step has been done in excel, including combining 20 years of data, and set up the win probability from Bookmaker Concensus model
bet_data_win_prob<- read.csv("~/UoA/Project A/bet_data_with_wprob.csv")

bet_data_win_prob <- bet_data_win_prob |>
  mutate(Date = dmy(Date))


bet_data_win_prob <- bet_data_win_prob |>
  filter (!is.na(bet_concensus_win_prob))


bet_data_win_prob <- bet_data_win_prob %>%
  mutate (higher_odd_win_prob = ifelse (bet_concensus_win_prob > 0.5,
                                        bet_concensus_win_prob,
                                        1- bet_concensus_win_prob))
```


## MERGE BETTING DATA WITH ELO DATA
```{r}

## MERGE BETTING DATA WITH ELO DATA


merge_elo <- tennis %>%
  filter (tourney_date >= dmy("01-01-2000")) %>% #Filtered to match the data date, as bet data only available from 2000 onward
  dplyr::rename(WRank = winner_rank, LRank = loser_rank)

merge_elo <- data.table(merge_elo)

merge_bet <- bet_data_win_prob 

merge_bet <- data.table(merge_bet)


setkey(merge_elo,WRank,LRank,tourney_date)

## Merging data using player ranking at the time of the match, rolling back 14 days
### This is done since ELo data uses tournament starting date, while betting date has the exact match day, and tournament typically last for 2 weeks

merge_bet[,mergerdate:=Date]

setkey(merge_bet,WRank,LRank,mergerdate)

merge_data <- merge_bet[merge_elo,roll=-14]


merge_data <- merge_data %>%
  drop_na(Date) %>%
  arrange(Date, Location)


```

## VALIDATION FUNCTION
```{r}

## VALIDATION FUNCTION

### FOR ELO

run_elo_validation <- function (input_data) {
  
  input_data <- input_data %>%
    mutate (higher_elo_win_prob = ifelse (winner_pre_elo > loser_pre_elo,
                                          calculate_expected_score(winner_pre_elo, loser_pre_elo),
                                          calculate_expected_score(loser_pre_elo, winner_pre_elo)))
    
  input_data <- input_data %>%
    mutate (higher_elo_win = ifelse (winner_pre_elo > loser_pre_elo, 1,0))
  
  
  N_ELO <- nrow(input_data)

  W_ELO <- input_data$higher_elo_win
  
  
  calibration_elo <- sum(input_data$higher_elo_win_prob) / sum(input_data$higher_elo_win)
  
  preds_elo <- ifelse (input_data$higher_elo_win_prob > 0.5, 1, 0)
  
  accuracy_elo <- mean(preds_elo == input_data$higher_elo_win)
  
  
  log_loss_elo <- (-1 / N_ELO) * sum(W_ELO * log(input_data$higher_elo_win_prob) + 
                                       (1 - W_ELO) * log(1 - input_data$higher_elo_win_prob), na.rm = T)
  
  return(c(accuracy_elo,
           log_loss_elo,
           calibration_elo))
}  
  

### FOR BETTING DATA
run_bet_validation <- function (input_data) {

  N_bet <- nrow(input_data)
  
  
  W_bet<- input_data$higher_odd_win
  
  
  
  
  calibration_bet <- sum(input_data$higher_odd_win_prob) / sum(input_data$higher_odd_win)
  
  preds_bet <- ifelse (input_data$higher_odd_win_prob > 0.5, 1, 0)
  
  accuracy_bet <- mean(preds_bet == input_data$higher_odd_win,  na.rm = T)
  
  
  log_loss_bet <- (-1 / N_bet) * sum(W_bet * log(input_data$higher_odd_win_prob) + 
                                       (1 - W_bet) * log(1 - input_data$higher_odd_win_prob), na.rm = T)
    
  return(c(accuracy_bet,
           log_loss_bet,
           calibration_bet))
    
}
```



## SeT UP GLICKO DATA
```{r}
### SeT UP GLICKO DATA - note: we used the PlayerRatings package for Glicko, so there are several steps for this calculation, it's probably best to re-built the model on our own for better calculation.

test_data_glicko <- tennis

## create a year-month, convert to numeric
test_data_glicko <- test_data_glicko %>%
  mutate (year_month = format(tourney_date, "%Y - %m")) %>%
  mutate (period_by_month = as.numeric(ym(year_month)))


## create a cross check table of year-month and its numeric period
cross_table <- test_data_glicko %>%
  select(tourney_date) %>%
  mutate(year_month = format(tourney_date, "%Y - %m")) %>%
  distinct(year_month) %>%
  rowid_to_column("period")


# Merge to get the period sequence
test_data_glicko_2 <- merge(test_data_glicko, cross_table, by = "year_month")


# Set up the data that go in to the model
test_data_glicko_in <- test_data_glicko_2 %>%  
  select (period, winner_id, loser_id) %>%
  mutate (player_one_win = 1)

```


## GLICKO RELATED FUNCTIONS
```{r}
### Function to predict winning probability in Glicko

glicko_win_prob <- function (rating_a, rating_b, rd_a, rd_b, t_a = 1, t_b = 1, c = 15) {
  q = log(10) / 400
  
  
  rd_a = min(sqrt(rd_a^2 + (c^2)*t_a),350)
  rd_b = min(sqrt(rd_b^2 + (c^2)*t_b),350)
  
  rd_comb = (sqrt(rd_a^2 + rd_b^2))
  
  g.RD = 1/ (sqrt (1 + (3*(q^2)*rd_comb^2)/(pi^2)))
  
  
  E = 1/ (1+ 10^ (-g.RD*(rating_a - rating_b)/400))
  
  return (E)
}
```


```{r}
### Function to run throught the data, grab info from the predicted table, then calculate winning probability
run_glicko_prediction <- function (input_data, glicko_rating_output, cval) {
  
  
  for (i in 1:nrow(input_data)) {
    ## Set up winner and loser 
    winner <- input_data$winner_id[i]
    loser <- input_data$loser_id[i]
    
    
    ## Set current period
    current_period <- input_data$period[i]
    
    
    ## extract winner Elo, RD and total off time from the last period before the match
    input_data$winner_pre_elo[i] <-
      glicko_rating_output$history[,,1][as.character(winner),current_period-1]
    input_data$winner_pre_rd[i] <-
      glicko_rating_output$history[,,2][as.character(winner),current_period-1]
    input_data$winner_lag[i] <-
      glicko_rating_output$history[,,4][as.character(winner),current_period-1] + 1
    
    
    ## same for loser
    input_data$loser_pre_elo[i] <-
      glicko_rating_output$history[,,1][as.character(loser),current_period-1]
    input_data$loser_pre_rd[i] <-
      glicko_rating_output$history[,,2][as.character(loser),current_period-1]
    input_data$loser_lag[i] <-
      glicko_rating_output$history[,,4][as.character(loser),current_period-1] + 1
    
    
    ## calculate the win probability
    input_data$prediction[i] <- glicko_win_prob(input_data$winner_pre_elo[i], 
                                                input_data$loser_pre_elo[i], 
                                                input_data$winner_pre_rd[i], 
                                                input_data$loser_pre_rd[i],
                                                t_a = input_data$winner_lag[i],
                                                t_b = input_data$loser_lag[i],
                                                c = cval)
  }
  
  return (input_data)
}


```




# RUN THE MODELS

## ORIGINAL ELO
```{r}
## ORIGINAL ELO RUN

##### WTIH FULL DATA
for (i in 20:50) { # k running from 20 to 50
  
  temp_output <- run_elo (tennis, k = i)
  
  saveRDS (temp_output, file = paste0("/org_elo/full_data/elo_k_", i, ".rds")) # save the final performance data
  
}


##### WITH MERGE DATA
for (i in 20:50) { # k running from 20 to 50
  
  temp_output <- run_elo (merge_data, k = i)
  
  saveRDS (temp_output, file = paste0("/org_elo/merge_data/elo_k_", i, ".rds")) # save the final performance data
  
}


## sample output file: elo_k_40.rds

```



## SURFACE ELO
```{r}
## Surface Elo Run (only for full data)

##### Carpet
for (i in 20:50) { # k running from 20 to 50
  
  temp_output <- run_elo (tennis_carpet, k = i)
  
  saveRDS (temp_output, file = paste0("/surface/full_data/carpet_elo_k_", i, ".rds")) # save the final performance data
  
}


##### Clay
for (i in 20:50) { # k running from 20 to 50
  
  temp_output <- run_elo (tennis_clay, k = i)
  
  saveRDS (temp_output, file = paste0("/surface/full_data/clay_elo_k_", i, ".rds")) # save the final performance data
  
}


##### Grass
for (i in 20:50) { # k running from 20 to 50
  
  temp_output <- run_elo (tennis_grass, k = i)
  
  saveRDS (temp_output, file = paste0("/surface/full_data/grass_elo_k_", i, ".rds")) # save the final performance data
  
}


##### Clay
for (i in 20:50) { # k running from 20 to 50
  
  temp_output <- run_elo (tennis_hard, k = i)
  
  saveRDS (temp_output, file = paste0("/surface/full_data/hard_elo_k_", i, ".rds")) # save the final performance data
  
}

```


## FTE ELO
```{r}
### FTE ELO RUN - innitial test show that nu = 5 is optimised, there for we only run through delta and sigma



##### WTIH FULL DATA
for (d in seq(200,300,10)) { # delta running from 200 to 300, step of 10
  for (s in seq(0.3,0.5,0.025)) { # sigma running from 0.3 to 0.5, step of 0.025
  
    temp_output <- run_elo (tennis, k = i)  run_elo_FTE(merge_data, delta = d, nu = 5, sigma = s)
    
    saveRDS (temp_output, file = paste0("/FTE/full_data/elo_FTE_delta_", d, "_nu_5_sigma_", s*100 ,".rds")) # save the final performance data
  }
}



##### WTIH MERGE DATA
for (d in seq(200,300,10)) { # delta running from 200 to 300, step of 10
  for (s in seq(0.3,0.5,0.025)) { # sigma running from 0.3 to 0.5, step of 0.025
  
    temp_output <- run_elo (merge_data, k = i)  run_elo_FTE(merge_data, delta = d, nu = 5, sigma = s)
    
    saveRDS (temp_output, file = paste0("/FTE/merge_data/elo_FTE_delta_", d, "_nu_5_sigma_", s*100 ,".rds")) # save the final performance data
  }
}

## sample output file: elo_FTE_delta_200_nu_5_sigma_30.rds

```



## GLICKO
```{r}
### GLICKO, using the PlayerRating package

for (c in seq(5,75,5)) { # cval running from 5 - 75, step of 5
  temp_output <- glicko(tennis, cval = c, history = TRUE)
  saveRDS (temp_output, file = paste0("/Glicko/glicko_c_", c, ".rds"))
}
```


# ANALYSING

## ORIGINAL ELO

### CALCULATE VALIDATION STATS
```{r}
validation_elo_train <- tibble(k = numeric(), pred_acc = numeric(),
                                    log_loss = numeric(), calibration = numeric())

for (k in 20:50) {
  
  
  tennis_train <- tennis
  
  tennis_train <- filter(tennis_train, tourney_date < split_time)
  
  split_time <- dmy("01-01-2019")
  matches_train_df <- filter(tennis, tourney_date < split_time)
  matches_test_df <- filter(tennis, tourney_date >= split_time)
  
  ## SET UP
  path <- paste0("~/org_elo/full_data/elo_k_",
                 k,
                 ".rds")
  
  org_elo_temp <- readRDS(path)[[1]]
  
  split_time <- dmy("01-01-2019")
  org_elo_train <- filter(org_elo_temp, tourney_date < split_time)
  org_elo_test <- filter(org_elo_temp, tourney_date >= split_time)
  
  
  validation_temp <- run_elo_validation(org_elo_train)
  
  validation_elo_train <- validation_elo_train %>%
    add_row(k = k, 
            pred_acc = validation_temp[1],
            log_loss = validation_temp[2], 
            calibration = validation_temp[3])
  
}
```


### CHART TO ANALYSE ORIGINAL ELO PERFORMANCE WITH DIFFERENT K

```{r}
p3 <- validation_elo_train %>%
  ggplot (aes (k)) +
  geom_line (aes (y = log_loss)) +
  geom_vline(xintercept =29, color = "red") +
  geom_text( x=31, y=0.59745, label = "k=29", color = "red", angle = 270) +
  labs ( x = "k value",
         y = "Log loss",
         title = "Log loss")


p2 <- validation_elo_train %>%
  ggplot (aes (k)) +
  geom_line (aes (y = calibration)) +
  geom_vline(xintercept =20, color = "red") +
  geom_text( x=22, y=1.028, label = "k=20", color = "red", angle = 270) +
  labs ( x = "k value",
         y = "Calibration",
         title = "Calibration")


p1 <- validation_elo_train %>%
  ggplot (aes (k)) +
  geom_line (aes (y = pred_acc)) +
  geom_vline(xintercept =34, color = "red") +
  geom_text( x=36, y=0.679, label = "k=34", color = "red", angle = 270) +
  labs ( x = "k value",
         y = "Accuracy",
         title = "Accuracy")


figure_k_value <- (p1 | p2 | p3)
```



## SURFACE ELO

```{r}
validation_elo_train <- tibble(k = numeric(), pred_acc = numeric(),
                                    log_loss = numeric(), calibration = numeric())

for (k in 20:50) {
  
  
  tennis_train <- tennis
  
  tennis_train <- filter(tennis_train, tourney_date < split_time)
  
  split_time <- dmy("01-01-2019")
  matches_train_df <- filter(tennis, tourney_date < split_time)
  matches_test_df <- filter(tennis, tourney_date >= split_time)
  
  ## SET UP
  path <- paste0("~/org_elo/full_data/elo_k_",
                 k,
                 ".rds")
  
  org_elo_temp <- readRDS(path)[[1]]
  
  split_time <- dmy("01-01-2019")
  org_elo_train <- filter(org_elo_temp, tourney_date < split_time)
  org_elo_test <- filter(org_elo_temp, tourney_date >= split_time)
  
  
  validation_temp <- run_elo_validation(org_elo_train)
  
  validation_elo_train <- validation_elo_train %>%
    add_row(k = k, 
            pred_acc = validation_temp[1],
            log_loss = validation_temp[2], 
            calibration = validation_temp[3])
  
}
```




## COMBINED ELO

### CALCULATING DATA


```{r}
split_time <- dmy("01-01-2019")
validation_comb_elo_train <- tibble(rate = numeric(), pred_acc = numeric(),
                                    log_loss = numeric(), calibration = numeric())

for (n in 1:9) {
  
  ## SET UP
  x = n*0.1
  
  w_e = paste0("combine_winner_elo_",x)
  
  l_e = paste0("combine_loser_elo_",x)
  
  
  ## Calculate the prob
  
  comb_elo_temp <- comb_elo %>%
    mutate (higher_comb_elo_win_prob = ifelse (get(w_e) > get(l_e),
                                               winprob(get(w_e), get(l_e)),
                                               winprob(get(l_e), get(w_e))))
  
  comb_elo_temp <- comb_elo_temp %>%
    mutate (comb_higher_elo_win = ifelse (get(w_e) > get(l_e), 1,0))
  
  ## Take the pre 2019 data
  comb_elo_test <- filter(comb_elo_temp, tourney_date >= split_time)
  
  ## Calculate the metrics
  N <- nrow(comb_elo_test)
  
  W <- comb_elo_test$comb_higher_elo_win
  
  
  preds_elo_comb <- ifelse (comb_elo_test$higher_comb_elo_win_prob > 0.5, 1, 0)
  
  accuracy_elo_comb <- mean(preds_elo_comb == comb_elo_test$comb_higher_elo_win, na.rm = T)
  
  calibration_elo_comb = sum(comb_elo_test$higher_comb_elo_win_prob, na.rm = T) / 
    sum(comb_elo_test$comb_higher_elo_win, na.rm = T)
  
  log_loss_elo_comb <- (-1 / N) * 
    sum(W * log(comb_elo_test$higher_comb_elo_win_prob) + 
          (1 - W) * log(1 - comb_elo_test$higher_comb_elo_win_prob), na.rm = T)
  
  
  validation_comb_elo_train <- validation_comb_elo_train |>
    add_row(rate = x, pred_acc = accuracy_elo_comb,
            log_loss = log_loss_elo_comb, calibration = calibration_elo_comb)
  
}
```


### CHART TO ANALYSE PERFORMANCE

```{r}
p5 <- validation_comb_elo_train %>%
  ggplot (aes (rate)) +
  geom_line (aes (y = pred_acc)) +
  geom_vline(xintercept = 0.6, color = "red") +
  geom_text( x=0.65, y=0.6777, label=TeX("$\\lambda=0.6"), color = "red", angle = 270) +
  labs ( x = TeX("$\\lambda value"),
         y = "Accuracy",
         title = "Accuracy")


p6 <- validation_comb_elo_train %>%
  ggplot (aes (rate)) +
  geom_line (aes (y = calibration)) +
  geom_vline(xintercept = 0.4, color = "red") +
  geom_text( x=0.45, y=1.012, label=TeX("$\\lambda=0.4"), color = "red", angle = 270) +
  labs ( x = TeX("$\\lambda value"),
         y = "Calibration",
         title = "Calibration")


p7 <- validation_comb_elo_train %>%
  ggplot (aes (rate)) +
  geom_line (aes (y = log_loss))  +
  geom_vline(xintercept = 0.6, color = "red") +
  geom_text( x=0.65, y=0.587, label=TeX("$\\lambda=0.6"), color = "red", angle = 270) +
  labs ( x = TeX("$\\lambda value"),
         y = "Log loss",
         title = "Log loss")



validation_comb_elo_chart <- (p5 | p6 | p7)
```



